%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{WORK EXPERIENCE}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventrytwo
    {Backend Engineer} % Job title
    {Ahrefs} % Organization
    {Singapore} % Location
    {Jul. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated complex billing gateways to Stripe enhancing revenue accuracy, customer satisfaction, and operational efficiency while mitigating compliance risks.}
        \item {Build and maintain reliable backend features for our SERPs services that need to run continuously and provide low-latency data retrieval allowing thousands of positions metrics to be queried in seconds.} %
        \item {Enhanced internal tooling for seamless Slack workspace integration, improving usability across desktop and mobile.}
        \item {Actively contributed to the OCaml opensource community, enhancing developer experience through projects like \href{https://github.com/ahrefs/slack}{Slack API wrapper library}.}
        % \item {Participate in code review to ensure code quality.}
        % \item {Heavily engaged with code reviews to produce clean code which significantly increase maintainability.}
      \end{cvitems}
    }
    {Backend Intern} % Job title
    {Oct. 2022 - Apr. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and implemented new features for \href{https://github.com/ahrefs/monorobot}{monorobot} which allows for richer control over notifications from monorepos to Slack.}
        \item {Rewritten internal orchestration tool from Javascript and bash into OCaml improving its concurrency guarantees, maintainability, and reliability.}
        \item {Consolidate uses of Slack APIs into an \href{https://github.com/ahrefs/slack}{opensource library}, which removes thousands of lines in duplicated code, significantly increasing maintainability.}
        % \item {Heavily engaged with code reviews to produce clean code which significantly increase maintainability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {APAC Technology and Change Summer Analyst (Developer Experience Team)} % Job title
    {Credit Suisse} % Organization
    {Singapore} % Location
    {May. 2022 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built long-running compliance checking services in Golang Gin that can recover easily to give peace of mind and help to prevent legal actions.}
        \item {Heavily practiced test-driven development (TDD) to significantly increase maintainability and development speed by incorporating at least 95\% coverage for each Go package in the services using unit tests.}
        \item {Designed and maintained a full suite of integrated tests for a variety of scenarios ensuring all critical failures in our GitLab ecosystem are caught early and built many utilities for faster future tests development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer Intern, Technical Architecture (Message Queue Team)} % Job title
    {ByteDance} % Organization
    {Singapore} % Location
    {Jan. 2022 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enriched company wiki to ensure newcomers take less time getting up to speed on the system.}
        \item {Designed and built low-level long-running test services in Java that can recover easily so integration test cases are always up to ensure critical system bugs are caught in early stages and prevent catastrophic failures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {BeLive Technology} % Organization
    {Singapore} % Location
    {Jan. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full-stack development for analytics dashboard of streaming solutions that provide concrete feedback and drive business strategies for their live-streaming solutions.}
        \item {Developed multi-threaded backends in different lightweight frameworks (Python Flask, C++ Crow) to provide highly available service.}
        \item {Facilitated seamless DevOps using Docker with Nginx that improved team backend reliability and portability to AWS and Google Cloud.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  %% \cventry
  %%   {Research Assistant} % Job title
  %%   {NUS, Faculty of Engineering} % Organization
  %%   {Singapore} % Location
  %%   {Aug. 2020 - Jan. 2021} % Date(s)
  %%   {
  %%     \begin{cvitems} % Description(s) of tasks/responsibilities
  %%       \item {Designed and setup data pipeline for processing with HPC and communicate effective team guidelines to improve productivity.}
  %%       \item {Work with geo-spatial data to create models that can accurately predict port boundaries to increase team’s capabilities to study GHG emissions and further advice government policy-making.}
  %%     \end{cvitems}
  %%   }
    
%---------------------------------------------------------
  % \cventry
  %   {DxI (Predictive Intelligence) Intern} % Job title
  %   {Edelman} % Organization
  %   {Singapore} % Location
  %   {Jun. 2020 - Jul. 2020} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Ran EDA to inform better feature selection and engineering using NLP techniques which increased the effectiveness of the baseline model allowing thought leadership opportunity that drives business strategies.  Assisted in a variety of projects in different industries including financial, and pharmaceuticals.}
  %     \end{cvitems}
  %   }
    
%---------------------------------------------------------
  \cventry
    {Computational Biology Research Assistant} % Job title
    {Yale-NUS College} % Organization
    {Singapore} % Location
    {Aug. 2019 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed new functions to optimize linear programming processes and for better user experience through control over such processes. Migrated the software from Python 2.7 to Python 3.4 with detailed commits using GitHub.}
        \item {Maintained and managed intranet VMs for running models and helped with IDM for new students.  Train new student developers in best practices and help build and project-manage for new feature developments for the scobra library.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
